Assessing paravascular transport in the parenchyma by partial differential equation (PDE) constrained optimization

### 2018-10-28 tex/paper.tex
update

%The recently proposed glymphatic system propose a new mechanism for waste
%clearance from the brain and has opened for a new paradigm in        
%research on Alzheimer's disease where one of the defining features
%is that metabolic waste accumulate within the brain. The glymphatic system is still controversial and while
%experimental investigations in rodents as well as novel MRI investigations in humans
%provide evidence for the existence of this system, a proper theoretical
%foundation is currently missing from the bio-mechanical point of view. In particular,
%a crucial question in the current debate is how much the system accelerate
%waste clearance when compared to extra-cellular diffusion alone. In this paper,
%we will therefore evaluate to what extent partial differential constrained optimization methods
%can be used to identify modeling parameters for glymphatic transport when we    
%assume that the underlying equation can be represented by a diffusion equation
%representing extra-cellular diffusion and possibly dissipation caused by the glymphatic system.
\end{abstract}
\section{Introduction}
In 2012, ~\citet{iliff2012paravascular} provided evidence for a a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes. It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain. Evidence was given that the activity of the glymphatic system increases during sleep ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain. The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease. Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 \citet{eide2015mri}, and in 2017 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.

>>>>

%The recently proposed glymphatic system propose a new mechanism for waste
%clearance from the brain and has opened for a new paradigm in        
%research on Alzheimer's disease where one of the defining features
%is that metabolic waste accumulate within the brain. The glymphatic system is still controversial and while
%experimental investigations in rodents as well as novel MRI investigations in humans
%provide evidence for the existence of this system, a proper theoretical
%foundation is currently missing from the bio-mechanical point of view. In particular,
%a crucial question in the current debate is how much the system accelerate
%waste clearance when compared to extra-cellular diffusion alone. In this paper,
%we will therefore evaluate to what extent partial differential constrained optimization methods
%can be used to identify modeling parameters for glymphatic transport when we    
%assume that the underlying equation can be represented by a diffusion equation
%representing extra-cellular diffusion and possibly dissipation caused by the glymphatic system.
\end{abstract}
\section{Introduction}
In 2012, ~\citet{iliff2012paravascular} provided evidence for a a brain-wide paravascular system, denoted the glymphatic system, which is a pathway for transport of fluids and solutes. It was proposed to have an important metabolic role by providing a pathway for clearance of waste solutes from the brain. Evidence was given that the activity of the glymphatic system increases during sleep ~\citet{xie2013sleep}, thus linking sleep to clearance of toxic substances from the brain. The glymphatic system seems to become impaired during aging, and failure of the glymphatic system may play a role in neurodegenerative disease and development of Alzheimer's disease. Evidence for a brain-wide glymphatic system in humans was first obtained in 2015 \citet{eide2015mri}, and in 2018 \citet{ringstad2018brain} provided evidence that glymphatic function is deteriorated in individuals with dementia, as compared to controls.
Several aspects of the glympahtic system are still debated, for example whether glymphatic transport of solutes is by convective mechanisms or by diffusion.
